Outcomes

### 2023-10-18 analysis/aggressive_care.qmd
changes
Added setup.R script

---
title: "Aggressive Care and Hemispheric Laterality"
---

```{r setup}
#| code-fold: true
#| code-summary: "Setup"
#| warning: false
#| message: false

library(tidyverse) # ggplot, dplyr, and friends
library(janitor)
library(glue) # Easier string interpolation
library(gt) # Fancy tables
library(scales) # Nicer labeling functions
library(patchwork) # Combine plots nicely
library(ggmosaic) # Mosaic plots with ggplot
library(parameters) # Extract model parameters as data frames
library(cmdstanr) # Run Stan code from R
library(brms) # Nice frontend for Stan
library(tidybayes) # Manipulate MCMC chains in a tidy way
library(here)

# Set some global Stan options
CHAINS <- 4
ITER <- 2000
WARMUP <- 1000
BAYES_SEED <- 160
options(mc.cores = parallel::detectCores(), brms.backend = "cmdstanr")

# ggplot theming
theme_nice <- function() {
  theme_minimal(base_family = "Cantarell") +
    theme(
      panel.grid.minor = element_blank(),
      plot.title = element_text(family = "Cantarell", face = "bold"),
      axis.title = element_text(family = "Cantarell Medium"),
      axis.title.x = element_text(hjust = 0),
      axis.title.y = element_text(hjust = 1),
      strip.text = element_text(
        family = "Cantarell", face = "bold",
        size = rel(1), hjust = 0
      ),
      strip.background = element_rect(fill = NA, color = NA)
    )
}

>>>>

---
title: "Aggressive Care and Hemispheric Laterality"
---
{{< include 00-setup.qmd >}}

### 2023-10-18 analysis/outcomes.qmd
changes
Added setup.R script

```{r setup, warning=FALSE, message=FALSE}

library(tidyverse)
library(marginaleffects)
library(brms)
library(cmdstanr)
library(tidybayes)
library(parameters)
library(broom)
library(broom.mixed)
library(ggdist)
library(here)

# seeds
set.seed(160)
BAYES_SEED <- 160

# Bayes
options(
  mc.cores = parallel::detectCores(),
  brms.backend = "cmdstanr"
)

data <- read_rds(here("data", "all.rds"), refhook = NULL)

data <- data |>
  filter(ich_location == "Basal Ganglia" | ich_location == "Thalamus" | ich_location == "Lobar") |>
  select(study, age, ich_laterality, ich_location, ich_volume_baseline, gcs_baseline, ivh, neurosurgery_evac, sbp_baseline, mrs_90_01, mrs_90_02, mrs_90_03, mrs_90_04, mrs_90) |>
  drop_na(ich_laterality)

data$ich_location <- fct_drop(data$ich_location)
data$ich_laterality <- fct_drop(data$ich_laterality)

data_erich_atach <- data |>
  filter(study == "ERICH" | study == "ATACH2")

# plot stuff
theme_set(theme_minimal(base_family = "Noah"))

@@

```{r brms priors}

>>>>

{{< include 00-setup.qmd >}}

@@

```{r brms priors, warning=FALSE, message=FALSE}
